References

### 2017-04-07 cv/20sec/template.tex
Revised my CV.

@@

\aboutme{
  \begin{itemize}
  \item Ph.D of Mathematical Statistics at Copenhagen University
  \item M.Sc. of Mathematical Physics
  \item M.Sc. of Computer Science
  \item 7 years work experience in programming 
  \item strong in statistical analysis \& numerical methods
  \end{itemize}
} % To have no About Me section, just remove all the text and leave \aboutme{}

@@

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills {{Python/3},{SQL/4},{Matlab/5.2},{GNU Scientific Library/5},{R/5.8},{Parallel Computing OpenMP/4.5},{C/5},{C++/5}}

@@

\begin{minipage}{0.15\linewidth}
  Oct. 2014 - Sep. 2017
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item Ph.D. in Mathematical Statistics
  \item Copenhagen University
  \item Areas of research:
    \begin{itemize}
      \item {\bf Time series analysis}: ARIMA, GARCH, stochastic volatility
        models
      \item {\bf Asset allocation \& risk management}: Principle component
        analysis; optimization of investor utility functions; extreme
        value theory
      \item {\bf Numerical methods}: Importance sampling, numerical
        optimization, estimation of GARCH(p,q) tail indices
    \end{itemize}
  \end{itemize}
\end{minipage}

@@

\begin{minipage}{0.15\linewidth}
  Sep. 2011 - June 2014
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item M.Sc. in Mathematical Physics
  \item Lund University
  \item Thesis project: Distribution of eigenvalues of large
    sample covariance matrices in the infinite dimensional limit with
    a focus on the influence of autocorrelations and heavy tails. The
    theoretical derivation is based on the {\it free probability
      theory} and is checked against {\it intraday tick-by-tick
      prices} of high-volume Swedish stocks.
  \item Course work:    
    \begin{itemize}
      \item Mathematical methods of Physics and Engineering
      \item Statistical mechanics, Quantum mechanics, General
        relativity
    \end{itemize}
  \end{itemize}
\end{minipage}

@@

\begin{itemize}
\item Davis, R.A., Heiny, J., Mikosch, T. and {\bf Xie, X.},
  2016. {\it Extreme value analysis for the sample autocovariance
    matrices of heavy-tailed multivariate time series}.
  \underline{Extremes}, 19(3), pp.517-547.

@@

\item Jan\ss en, A., Mikosch, T., Rezapour, M., {\bf Xie, X},
  2016. {\it The eigenvalues of the sample covariance matrix of a
    multivariate heavy-tailed stochastic volatility model}.
  To appear in the \underline{Bernoulli Journal}.

@@

\section{Papers in Finalization}
\begin{itemize}
\item Mikosch, T., de Vries, C., {\bf Xie, X.}, 2017,
  {\it Tail-indices and scale parameters of returns series}

  {\small
    %% We study the heavy tail properties of real-world equity return
    %% distributions and, based on the framework of Generalized
    %% Disappointment Aversion, derive how an investor's preference varies
    %% with the tail distribution characteristics, namely the tail index and
    %% the scale parameter. We find, when the equity return is t-distributed,
    %% the GDA preference actually decreases with the degree of freedom of
    %% the distribution, i.e. the tail index; we interprete this as a
    %% consequence of the symmetry of the distribution. When the equity
    %% return is assumed to have a shifted Pareto distribution with
    %% independent parameters of the left and the right tails, we find the
    %% GDA preference increasing with both the lower tail index and the scale
    %% parameter. We attribute this to the risk avert nature of rational
    %% investors. By numerical methods, optimal asset allocation is also
    %% solved in both cases.
    It is a stylized fact that equity return distributions are
    heavy-tailed. We discuss how an investor's preference of an equity
    varies with the parameters of the tail distribution of the return on
    equity. These parameters can be seen as characteristics of the
    market and provide a quantitative description of the status of the
    market.
    In addition, we also find optimal asset allocation schemes
    corresponding to different investor preferences as captured by the
    investors' utility functions. These results can be useful when
    considering a problem of asset allocation. Real-world stock return
    series, which have motivated our work, are analyzed and presented.
  }
\end{itemize}
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

@@

\newpage % Start a new page

\section{Work Experience}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{1900}{Alice in Wonderland-The Circra (1900's) Silent Film.}{Film}{The first Alice on film was over a hundred years ago.}
	\twentyitem{1933}{Alice in Wonderland 1933 version.}{Film}{This film stars Ethel griffies and Charlotte Henry. It was a box office flop when it was released.}
	\twentyitem{1951}{Disney Film.}{Film}{Walt Disney brings Lewis Carroll's fantasy story to life in this well done animated classic. Even though many elements from the book were dropped, such as the duchess with the baby pig and mock turtle, this version is without a doubt the most famous Alice adaption made.}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

\section{Other information}

\subsection{Review}

Alice approaches Wonderland as an anthropologist, but maintains a
strong sense of noblesse oblige that comes with her class status. She
has confidence in her social position, education, and the Victorian
virtue of good manners. Alice has a feeling of entitlement,
particularly when comparing herself to Mabel, whom she declares has a
``poky little house," and no toys. Additionally, she flaunts her
limited information base with anyone who will listen and becomes
increasingly obsessed with the importance of good manners as she deals
with the rude creatures of Wonderland. Alice maintains a superior
attitude and behaves with solicitous indulgence toward those she
believes are less privileged.

%\section{Other information}

%\subsection{Review}

%Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a ``poky little house," and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

>>>>

%----------------------------------------------------------------------------------------
\newenvironment{aperiod}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{1em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

@@

\aboutme{
  \begin{itemize}
  \item Ph.D of Mathematical Statistics at Copenhagen University
  \item M.Sc. of Mathematical Physics
  \item M.Sc. of Computer Science
  \item 6.5 years work experience in programming 
  \item strong in statistical analysis \& numerical methods
  \end{itemize}
} % To have no About Me section, just remove all the text and leave \aboutme{}

@@

% Skill bar section, each skill must have a value between 0 an 6 (float)
\skills {{Java/3},{Python/3},{SQL/4},{Matlab/5.2},{GNU Scientific Library/5},{R/5.8},{Parallel Computing OpenMP/4.5},{C/5},{C++/5}}

@@

\begin{minipage}{0.15\linewidth}
  Oct. 2014 - Sep. 2017
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{Ph.D. in Mathematical Statistics}
  \item Copenhagen University, Denmark
  \item Areas of research:
    \begin{itemize}
      \item {\bf Time series analysis}: ARIMA, GARCH, stochastic volatility
        models
      \item {\bf Asset allocation \& risk management}: Principle component
        analysis; optimization of investor utility functions; extreme
        value theory
      \item {\bf Numerical methods}: Importance sampling, numerical
        optimization, estimation of GARCH(p,q) tail indices
    \end{itemize}
  \end{itemize}
\end{minipage}

@@

\begin{minipage}{0.15\linewidth}
  Sep. 2011 - June 2014
\end{minipage} \hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{M.Sc. in Mathematical Physics}
  \item Lund University, Sweden
  \item Thesis project: Distribution of eigenvalues of large
    sample covariance matrices in the infinite dimensional limit with
    a focus on the influence of autocorrelations and heavy tails. The
    theoretical derivation is based on the {\it free probability
      theory} and is checked against {\it intraday tick-by-tick
      prices} of high-volume Swedish stocks.
  \item Course work:    
    \begin{itemize}
      \item Mathematical methods of Physics and Engineering
      \item Statistical mechanics, Quantum mechanics, General
        relativity
    \end{itemize}
  \end{itemize}
\end{minipage}
\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2005 - June 2008
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{M.Sc.Computer Science and Engineering}
  \item Helsinki University of Technology
  \item {\it Major Subject:} Mobile Computing - Services and Security
  \item {\it Average grade:} 4.17/5.
  \end{itemize}
\end{minipage}
\vspace{3mm}

\begin{minipage}{0.15\linewidth}
  Sep. 2001 - June 2005
\end{minipage}\hfill
\begin{minipage}{0.85\linewidth}
  \begin{itemize}
  \item \underline{B.Sc.Computer Science and Engineering}
  \item Beijing Institute of Technology
  \end{itemize}
\end{minipage}

@@

\begin{itemize}
\item {\bf Xie, X.}, Davis, R.A., Heiny, J. and Mikosch, T.
  2016. {\it Extreme value analysis for the sample autocovariance
    matrices of heavy-tailed multivariate time series}.
  \underline{Extremes}, 19(3), pp.517-547.

@@

\item {\bf Xie, X}, Jan\ss en, A., Mikosch, T. and Rezapour, M.
  2016. {\it The eigenvalues of the sample covariance matrix of a
    multivariate heavy-tailed stochastic volatility model}.
  To appear in the \underline{Bernoulli Journal}.

@@

\section{Papers in Finalization}
\begin{itemize}
\item {\bf Xie, X.}, Mikosch, T. and de Vries, C., 2017,
  {\it Tail-indices and scale parameters of returns series}

  {\small
    It is a stylized fact that equity return distributions are
    heavy-tailed. We discuss how an investor's preference of an equity
    varies with the parameters of the tail distribution of the return on
    equity. These parameters can be seen as characteristics of the
    market and provide a quantitative description of the status of the
    market.
    In addition, we also find optimal asset allocation schemes
    corresponding to different investor preferences as captured by the
    investors' utility functions. These results can be useful when
    considering a problem of asset allocation. Real-world stock return
    series, which have motivated our work, are analyzed and presented.
  }
\end{itemize}

\pagebreak
\makeprofile % Print the sidebar

\section{Papers in Finalization}
\begin{itemize}
\item {\bf Xie, X.} Collamore, J, 2017
  {\it An efficient estimator of the probability of very large losses posed by
    GARCH(p,q) processes}

  {\small
    We propose an efficient importance sampling estimator of the
    probability of excursion over high thresholds (causing large
    losses) by Multivariate Markov chains e.g. a GARCH(p,q) process or
    a multivariate GARCH process.
    Although stationary distributions of these processes are known
    to have power-law tails, precise evaluation of the tail
    probabilities is difficult because the exact distribution is
    unknown. Moreover, naive simulation methods lead to erractic
    estimates. Our importance sampling estimator presents a solution.
  }
\end{itemize}
%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

@@

% \newpage % Start a new page

% \makeprofile % Print the sidebar

\section{Work Experience}
% \begin{twenty} % Environment for a list with descriptions
% 	\twentyitem{1900}{Alice in Wonderland-The Circra (1900's) Silent Film.}{Film}{The first Alice on film was over a hundred years ago.}
% 	\twentyitem{1933}{Alice in Wonderland 1933 version.}{Film}{This film stars Ethel griffies and Charlotte Henry. It was a box office flop when it was released.}
% 	\twentyitem{1951}{Disney Film.}{Film}{Walt Disney brings Lewis Carroll's fantasy story to life in this well done animated classic. Even though many elements from the book were dropped, such as the duchess with the baby pig and mock turtle, this version is without a doubt the most famous Alice adaption made.}
% 	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
% \end{twenty}
\begin{aperiod}
%% \begin{small}
\item {\it \href{http://www.stericsson.com}{\tt
      ST-Ericsson, Lund, Sweden}, Audio, Multimedia, Development
    Engineer, Sep 2008 - Jan 2011}

  My responsibilities included developing audio low-level software,
  typically device drivers, in the Linux OS. This involved designing and
  implementing data structures and procedures so that the hardware
  devices were used in the optimal way, in terms of parallelism,
  power consumption, robustness, and ease of maintenance.

  {\it C, C++, Java, Linux}
\item {\it \href{http://www.hiit.fi}{\tt Helsinki
      Institute of Information Technology, Helsinki}, Oct 2007 - May 2008}

  Funded by HIIT, I wrote my thesis ``A Mutual authentication and Key
  Agreement Protocol for the UMTS Network''. The algorithm of my
  protocol proposal was based on the Diffie-Hellman Exchange, but had
  significant modifications and extensions so that the mutual
  authentication between the mobile user and the network was delegated
  to the serving instead of the home network. The protocol design
  incorporated puzzle schemes that demanded unbalanced computing
  resources on the two sides to mitigate Denial-of-Service attacks.

  {\it C, C++, Linux}
\item {\it
    \href{http://www.goodmillsystems.com}{\tt Goodmillsystems,
      Helsinki}, Software Designer, May 2007 - Sep 2007}

  I developed a daemon program that ran on the company's smart router
  product to collect statistical data about the router's network
  traffic. The emphasis of the program was high performance in the
  context of competing read and write accesses.

  {\it C, C++, Linux}
\item {\it \href{http://www.cardinal.fi/}{\tt
      Cardinal Information Systems, Helsinki}, Software
    Developer, Sep 2006 - April 2007}

  I implemented the FLUTE protocol for the company's DVB-H
  mobile-end middleware. The implementation was multi-threaded and was
  built on the {\it pthread} library. Good performance and robustness
  were crucial requirements on the implementation.

  {\it C, C++, Linux}
\item {\it
    \href{http://www.digitalchocolate.com/}{\tt Digital Chocolate,
      Helsinki, Finland}, Game Engineer, Feb 2006 - Sep 2006}

  My responsibilities were porting and customizing mobile
  phone games for various handsets.

  {\it Java, J2ME, Bash}
\item {\it {\tt Beijing Holystone Ltd, Beijing}, Software
    Engineer, April 2004 - June 2005}

  I developed JSP pages and database routines for
  the company's information system.

  {\it Java, J2EE}
%% \end{small}
\end{aperiod}

\section{Interests}
\begin{itemize}
\item Algorithmic trading, alpha generation
\item statistical inference, machine learning, neural network
\end{itemize}
